\documentclass[a4paper,10pt]{article}

\addtolength{\topmargin}{-30pt}
\addtolength{\textheight}{60pt}
\addtolength{\oddsidemargin}{-60pt}
\addtolength{\textwidth}{120pt}

\begin{document}

\begin{center}
{\bf \LARGE Curriculum Vitae}
\end{center}

\vspace{1cm}

\subsection*{Maurizio Filippone}
\begin{description}
%\item Nationality:        Italian
\item 
  {\bf Lecturer} with the School of Computing Science, University of Glasgow.
\item Email:              maurizio.filippone@glasgow.ac.uk
\item Web Page:           www.dcs.gla.ac.uk/$\sim$maurizio/
\end{description}

\subsection*{Education}
\begin{itemize}
\item 2008 - PhD in Computer Science - University of Genova \\
Thesis title: Central Clustering in Kernel-Induced Spaces \\
Thesis topics: kernel methods for clustering, spectral clustering, relational clustering, fuzzy clustering.

\item 2004 - Master's Degree in Physics (full marks: 110/110) - University of Genova \\
Thesis title: Ensemble methods for time series analysis and forecasting \\
Thesis topics: Non linear systems, regression, ensemble of learning machines, signal processing.
\end{itemize}

\subsection*{Relevant Fellowships}
\begin{itemize}
\item From 01-2010 to 08-2011:
  Department of Statistical Science - University College London (2010 with the Department of Computing Science - University of Glasgow) \\
%  Sir Alwyn Williams Building Lilybank Gardens, Glasgow, G12 8QQ - United Kingdom \\
  Grant: The Synthesis of Probabilistic Prediction \& Mechanistic Modelling within a Computational \& Systems Biology Context \\
%  Keywords: \\
  PI: Prof. Mark Girolami

\item From 03-2008 to 12-2009: 
  Department of Computer Science - University of Sheffield \\
  Grant: ALMS: Advanced Lifestyle Monitoring Systems \\
  Keywords: novelty detection, statistical testing, Bayesian inference in data modeling. \\
  PI: Dr G. Sanguinetti

\item From 03-2007 to 10-2007: 
  Department of Information and Software Engineering - George Mason University \\
  Grant: Detecting Suspicious Behavior in Reconnaissance Images \\
  Keywords: outlier detection, density estimation, relational clustering. \\
  PI, co-PI: Prof. D. Barbar\`a and Prof. C. Domeniconi
\end{itemize}

%\item From 07-2006 to 10-2006 \\
%  Consorzio Venezia Ricerche \\
%  Grant: Tide level forecasting in the lagoon of Venezia \\ 
%  Keywords: time series analysis and forecasting, regression, ensembles of learning machines. \\
%  PI: Prof. E. Canestrelli
%\end{itemize}

\subsection*{Teaching Activity}
\begin{itemize}
\item 2008 - Lab assistant (2 hours) 
  Bioinformatics - University of Sheffield

\item 2004-2005 - Lab assistant (52 hours)
  Neural Networks and Soft Computing - University of Genova
\end{itemize}


\subsection*{Awards}
\begin{itemize}
     \item Best paper published in 2008 in the journal Pattern Recognition:
%5       \\M. Filippone, F. Camastra, F. Masulli, and S. Rovetta.
       \textbf{A survey of kernel and spectral methods for clustering}.
       \emph{Pattern Recognition}, 41(1):176-190, January 2008.
%%       \\Manuscripts published in volume 41 (year 2008) have been judged by the Editors-in-Chief and the members of the Editorial and Advisory Boards of the journal based on the following criteria: originality of the contribution, presentation and exposition of the manuscript, and citations by other researchers.
\end{itemize}

\subsection*{Selected Publications}
%\subsubsection*{Journals}
\begin{itemize}
     \item  M. Filippone, G. Sanguinetti.
       \textbf{Approximate inference of the bandwidth in multivariate kernel density estimation}.
       \emph{Computational Statistics \& Data Analysis}, 55(12):3104-3122, 2011.
     \item  M. Filippone, G. Sanguinetti.
       \textbf{A Perturbative Approach to Novelty Detection in Autoregressive Models}.
       \emph{IEEE Transactions on Signal Processing}, 59(3):1027-1036, March 2011.
     \item L. Mohamed, B. Calderhead, M. Filippone, M. Christie, and M. Girolami.
       \textbf{Population MCMC methods for history matching and uncertainty quantification}.
       \emph{Computational Geosciences}. to appear.
     \item  M. Filippone, F. Masulli, and S. Rovetta.
       \textbf{Applying the possibilistic c-means algorithm in kernel-induced spaces}.
       \emph{IEEE Transactions on Fuzzy Systems}, 18(3):572-584, June 2010.
     \item  M. Filippone, F. Masulli, and S. Rovetta.
       \textbf{Simulated annealing for supervised gene selection}.
       \emph{Soft Computing}. to appear.
     \item  M. Filippone, G. Sanguinetti.
       \textbf{Information theoretic novelty detection}.
       \emph{Pattern Recognition}, 43(3):805-814, March 2010.
     \item  F. Camastra and M. Filippone.
       \textbf{A comparative evaluation of nonlinear dynamics methods for time series prediction}.
       \emph{Neural Computing and Applications}, 18(8):1021-1029, November 2009.
%     \item  M. Filippone, F. Masulli, and S. Rovetta.
%       \textbf{Clustering in the membership embedding space}.
%       \emph{International Journal of Knowledge Engineering and Soft Data Paradigms}. in press. 
%      \item  S. Rovetta, F. Masulli, M. Filippone.
%        \textbf{Soft ranking in clustering}.
%        \emph{Neurocomputing}, 72(7-9):2028-2031, March 2009.
     \item  M. Filippone.
       \textbf{Dealing with non-metric dissimilarities in fuzzy central clustering algorithms}.
       \emph{International Journal of Approximate Reasoning}, 50(2):363-384, February 2009.
     \item  M. Filippone, F. Camastra, F. Masulli, and S. Rovetta.
       \textbf{A survey of kernel and spectral methods for clustering}.
       \emph{Pattern Recognition}, 41(1):176-190, January 2008.
\end{itemize}

%\subsubsection*{Refereed Conference Proceedings}
\begin{itemize}
     \item  D. Barbar\'{a}, C. Domeniconi, Z. Duric, M. Filippone, E. Lawson, and R. Mansfield.
       \textbf{Detecting suspicious behavior in surveillance images}.
       \emph{In ICDM Workshops}, pages 891-900. IEEE Computer Society, 2008. 
%     \item  E. Canestrelli, P. Canestrelli, M. Corazza, M. Filippone, S. Giove, and F. Masulli.
%       \textbf{Local learning of tide level time series using a fuzzy approach}.
%       In \emph{IJCNN - International Joint Conference on Neural Networks}, Orlando - Florida, 12-17 August 2007.
%      \item  M. Filippone, F. Masulli, and S. Rovetta.
%        \textbf{Possibilistic clustering in feature space}.
%        In Francesco Masulli, Sushmita Mitra, and Gabriella Pasi, editors,
%        \emph{WILF}, volume 4578 of \emph{Lecture Notes in Computer Science}, pages 219-226. Springer, 2007.
     \item  M. Filippone, F. Masulli, S. Rovetta, S. Mitra, and H. Banka.
       \textbf{Possibilistic approach to biclustering: An application to oligonucleotide microarray data analysis}.
       In \emph{Computational Methods in Systems Biology}, 
       vol 4210 of \emph{Lecture Notes in Computer Science}, 312-322. 2006.
%      \item  M. Filippone, F. Masulli, and S. Rovetta.
%        \textbf{Supervised classification and gene selection using simulated annealing}.
%        In \emph{IJCNN - International Joint Conference on Neural Networks},
%        Vancouver - Canada, 16-21 July 2006.
\end{itemize}


\subsection*{Referee Activity for International Journals}
  Pattern Recognition (19),
  IEEE Transactions on Neural Networks (11), 
  Pattern Recognition Letters (9),
  IEEE Transactions on Signal Processing (4), 
  IEEE Signal Processing Letters (2), 
  IEEE Transactions on Pattern Analysis and Machine Intelligence (1), 
  Computational Intelligence (1),
  Neural Processing Letters (1),
  IEEE Transactions on Parallel and Distributed Systems (1),
  Soft Computing (1),
%   EURASIP Journal on Advances in Signal Processing (1),
%   Information Sciences (1).

\subsection*{Relevant Talks}
\begin{itemize}
\item 8 February 2011, University College London - \emph{Calibration of Oil Reservoir Simulation Codes}.
\item 13 October 2010, Royal Statistical Society - \emph{Discussion of the paper ``Riemann manifold Langevin and Hamiltonian Monte Carlo methods'' by M. Girolami and B. Calderhead}.
\item 11 November 2009, University of Edinburgh - 14 July, 2009, Columbia University - 21 January, 2009, University of Glasgow - \emph{Information Theoretic Novelty Detection}.
% \item 14 July, 2009, Columbia University - \emph{Information Theoretic Novelty Detection}.
% \item 21 January, 2009, University of Glasgow - \emph{Information Theoretic Novelty Detection}.
\item 3 March 2008, University of Milano - \emph{Central Clustering in Kernel-Induced Spaces}.
\item 27 September 2007, George Mason University - \emph{Kernel and Spectral Methods for Clustering}.
\end{itemize}

\subsection*{Main Conferences Attended}
 ICPR 2010, ISBA 2010, NIPS 2008, ICDM 2008, IJCNN 2007

\end{document}
